Mistriage

### 2019-05-30 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd
Add files via upload

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOAD FUNCTIONS, ENVIROMENT AND TABLES
source("functions/WorkTableCreator.R")
## Original results and UI tables
results <- readRDS("output/original.results.Rds")
result.tables <- readRDS("result.tables.Rds")
result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
## Create table for ease of data retrival
results.all.data <- WorkTableCreator(result.tables.data.frame)
## Sample characteristics table
# table.one <-

@@

  table.2 <- lapply(result.tables.data.frame, function(x) x[1:3,])
  table.2 <- lapply(table.2, function(result) {
             kable(result, format = "markdown")
             })

@@

  table.3 <- lapply(result.tables.data.frame, function(x) x[4:6,])
  table.3 <- lapply(table.3, function(result) {
             kable(result, format = "markdown")
             })

@@

  table.4 <- lapply(result.tables.data.frame, function(x) x[7:9,])
  table.4 <- lapply(table.4, function(result) {
             kable(result, format = "markdown")
             })

@@

![**Figure 1** High- and low volume centre data set. Initial split based on number of patients. Temporal split made using date of traumatic event.](fig1.jpg)

@@

```{r, echo = FALSE, results = "asis"} 
## Table 1 = Sample characteristics table
##result.tables
```

@@

**Table 2** Model validation performance  
```{r, echo = FALSE, results = "asis"} 
## Table 2 = Cropped to only show validation
table.2
```

@@

**Table** 3 Model transfer performance  
```{r, echo = FALSE, results = "asis"} 
## Table 3 = Cropped to only show transfer
table.3
```

@@

**Table 4** Comparison mistriage (Sample validation performance subtracted from transferred performance)  
```{r, echo = FALSE, results = "asis"} 
## Table 4 = Cropped to only show transfer differance
table.4
```

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOAD FUNCTIONS, ENVIROMENT AND TABLES
  ## Source functions
  source("functions/WorkTableCreator.R")
  ## Original results
  results <- readRDS("output/original.results.Rds")
  ## Compiled results with UI
  result.tables <- readRDS("result.tables.Rds")
  ## Compiled results with UI as data frame
  result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
  ## Create table for ease of data retrival
  results.all.data <- WorkTableCreator(result.tables.data.frame)
  ## Sample characteristics table
  # table.one <-

@@

  table.2 <- results.all.data[1:3,]
  rownames(table.2) <- c("Mistriage", "Undertriage", "Overtriage")

@@

  table.3 <- results.all.data[4:6,]
  rownames(table.3) <- c("Mistriage", "Undertriage", "Overtriage")

@@

  table.4 <- results.all.data[7:9,]
  rownames(table.4) <- c("Mistriage", "Undertriage", "Overtriage")

@@

![](fig1.jpg)  
**Figure 1: High- and low volume centre data set.** Initial split based on number of patients. Temporal split made using date of traumatic event.

@@

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1 = Sample characteristics table
##result.tables
```

@@

**Table 2. Model validation performance, i.e. performance when applied to the sample in which the model was created.** Data is presented as point estimates with 95% Uncertainty Intervals (95% UI).
```{r, echo = FALSE, results = "asis"} 
## Table 2
kable(table.2[,1:2], format = "markdown")
kable(table.2[,3:4], format = "markdown")
kable(table.2[,5:6], format = "markdown")
```

@@

**Table 3. Model transfer performance, i.e. performance when transferred to the other sample in the same data set. ** Data is presented as point estimates with 95% Uncertainty Intervals (95% UI).  
```{r, echo = FALSE, results = "asis"} 
kable(table.3[,1:2], format = "markdown")
kable(table.3[,3:4], format = "markdown")
kable(table.3[,5:6], format = "markdown")
```

@@

**Table 4. Comparison mistriage, i.e. sample validation performance subtracted from transferred performance.** Data is presented as point estimates with 95% Uncertainty Intervals (95% UI).  
```{r, echo = FALSE, results = "asis"} 
kable(table.4[,1:2], format = "markdown")
kable(table.4[,3:4], format = "markdown")
kable(table.4[,5:6], format = "markdown")
```
